Model details and results

### 2023-09-21 notebook/model-details.qmd
little typos

$$
\begin{align}
&\ \textbf{Registered provinces for INGO } i \\
\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_{i_j}, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
&\ \textbf{Model of outcome average} \\
% Put the huge equation in a nested \begin{aligned}[t] environment so that 
% \mathrlap{} can go around it so that the annotations in the priors can be 
% aligned closer to the math
\mu_i =&\ 
  \mathrlap{\begin{aligned}[t]
  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
  & \beta_{11}\ \text{Time since Januay 2017} + \beta_{12}\ \text{Year registered}
  \end{aligned}}\\[8pt]
&\ \textbf{Priors} \\
\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
\end{align}
$$

@@

The only new-to-me distribution here is the Dirichlet prior for the cutpoints, so I wrote a whole blog post about it here. This is a little confusing, though. `ordbetareg()` requires a three-element Dirichlet distribution that contains three columns of probabilities, one per submodel: the only-zero part, the between-zero-and-one part, and the only-one part. However, it doesn't use these three probabilities directly. Instead, it uses an [*induced* Dirichlet distribution](https://betanalpha.github.io/assets/case_studies/ordinal_regression.html) [@Kubinec:2022, p. 524], meaning that it works with the *boundaries between the categories* and not the Dirichlet columns themselves ([see here for more about that, plus some neat visualizations of the cutpoints](https://www.andrewheiss.com/blog/2023/09/18/understanding-dirichlet-beta-intuition/#bonus-later-addition-boundaries-between-categories)).

>>>>

$$
\begin{align}
&\ \textbf{Registered provinces for INGO } i \\
\text{Count of provinces}\ \sim&\ \operatorname{Ordered\,Beta}(\mu_i, \phi_y, k_{1_y}, k_{2_y}) \\[8pt]
&\ \textbf{Model of outcome average} \\
% Put the huge equation in a nested \begin{aligned}[t] environment so that 
% \mathrlap{} can go around it so that the annotations in the priors can be 
% aligned closer to the math
\mu_i =&\ 
  \mathrlap{\begin{aligned}[t]
  & \beta_0 + \beta_1\ \text{Issue[Arts and culture]} + \beta_2\ \text{Issue[Education]}\ +\\
  & \beta_3\ \text{Issue[Industry association]} + \beta_4\ \text{Issue[Economy and trade]}\ + \\
  & \beta_5\ \text{Issue[Charity and humanitarian]} + \beta_6\ \text{Issue[General]}\ + \\
  & \beta_7\ \text{Issue[Health]} + \beta_8\ \text{Issue[Environment]}\ + \\
  & \beta_9\ \text{Issue[Science and technology]} + \beta_{10}\ \text{Local connections}\ + \\
  & \beta_{11}\ \text{Time since Januay 2017} + \beta_{12}\ \text{Year registered}
  \end{aligned}}\\[8pt]
&\ \textbf{Priors} \\
\beta_0\ \sim&\ \operatorname{Student\,t}(\nu = 3, \mu = 0, \sigma = 2.5) && \text{Intercept} \\
\beta_{1..12}\ \sim&\ \mathcal{N}(0, 5) && \text{Coefficients} \\
\phi_y\ \sim&\ \operatorname{Exponential}(1 / 100) && \text{Variability in province count} \\
k_{1_y}, k_{2_y}\ \sim&\ \operatorname{Induced\,Dirichlet}(1, 1, 1), && \text{0–continuous and continuous–1 cutpoints} \\
&\ \quad \text{or } \bigl[P(\alpha_1), P(\alpha_1 + \alpha_2)\bigr] && \quad\text{(boundaries between 3 Dirichlet columns)}
\end{align}
$$

@@

The only new-to-me distribution here is the Dirichlet prior for the cutpoints, so [I wrote a whole blog post about it here](https://www.andrewheiss.com/blog/2023/09/18/understanding-dirichlet-beta-intuition/). This is a little confusing, though. `ordbetareg()` requires a three-element Dirichlet distribution that contains three columns of probabilities, one per submodel: the only-zero part, the between-zero-and-one part, and the only-one part. However, it doesn't use these three probabilities directly. Instead, it uses an [*induced* Dirichlet distribution](https://betanalpha.github.io/assets/case_studies/ordinal_regression.html) [@Kubinec:2022, p. 524], meaning that it works with the *boundaries between the categories* and not the Dirichlet columns themselves ([see here for more about that, plus some neat visualizations of the cutpoints](https://www.andrewheiss.com/blog/2023/09/18/understanding-dirichlet-beta-intuition/#bonus-later-addition-boundaries-between-categories)).
